\documentclass[11pt,a4paper,oneside]{report}
\usepackage[margin=0.25in]{geometry}
\usepackage{indentfirst}



\pagestyle{empty}

\renewcommand{\thesection}{1}

\begin{document}
\begin{center}
\LARGE{ \bf IROS 2012 Travel Fellowship Application }
%\Large{Daniel M. Lofaro \\ }
%\large{Electrical and Computer Engineering Dept. \\ Drexel University \\ Philadelphia PA, USA \\}
%\large{\tt dml46@drexel.edu }
\end{center}

\section*{Student Information}
\begin{itemize}
\item Name: Daniel M. Lofaro - Electrical and Computer Engineering Dept. Drexel University
\item Student Status: Full-time Ph.D Student (see attached file)
\item Status: United States Citizen (see attached file)
\item Email: \tt{dml46@drexel.edu}
\end{itemize}


\section*{Paper Information}
\begin{itemize}
\item Number: 1255
\item Title: \textit{Humanoid Throwing: Design of Collision-Free Trajectories with Sparse Reachable Maps}
\item Description: Design, simulation and hardware testing of a method to create collision-free throwing trajectories for high degree of freedom manipulators. 
\end{itemize}


\section*{Expected Impact on Professional Development}

Daniel M. Lofaro is a Ph.D. candidate and expected to graduate June 2012.  IROS travel support will enable him to (1) showcase exciting fundamental results that are a culmination of several years of doctoral work; (2) continue active participation in the RAS Student Activities Committee (SAC); and (3) meet with those who have expressed interest in hosting his Fulbright application.

First, Daniel's work is focused on humanoid whole-body motion planning.  His well-received Humanoids 2010 paper catalyzed an approach which laid the foundation of his dissertation.  The approach, buttressed with both simulation and experiments with a full-sized Hubo humanoid are the captured in the IROS 2012 paper.  IROS Travel Support will enable Daniel to present the work as well as share first-hand experiences working with a full-sized humanoid.  This is important because humanoid roboticists often depend on ``talking shop'' and exchanging tips.  

Second, for ICRA 2012, Daniel was the webmaster.  He served at both the Special Program Committee (SPC) meeting as well as a Registration Desk volunteer at the conference.  He worked closely with both the Program and General Chairs to host the ICRA Student Welcome Banquet.  Furthermore, Daniel's experience supporting the 2010 NATO Advanced Studies Institute (ASI) has helped him develop a network of dedicated group of graduate student roboticists throughout Europe.  IROS Travel Support will help Daniel to build upon these experiences and network to foster RAS Student Activities Committee growth and participation.

Third, upon completing his PhD, Daniel intends to further his academic training overseas.  Encouraged by professors from the NATO ASI and ICRA 2012, he is submitting his Fulbright application.  His plans are to meet these professors again at IROS 2012 to touch base and identify applications of his PhD work.  IROS Travel Support will help him make the best of this opportunity; most of the professors are based in Europe and said they'll attend IROS Portugal.  

The net effect is that IROS Travel Support will enable Daniel to impact his research community (humanoids), his peers (RAS Student Activities Committee) and international robotics effort (through the Fulbright).  Both ICRA 2012 Program Chair (Paul Oh) and General Chair (Nikos Papanikolopoulos) give Daniel much credit for his volunteering and are ready to give full recommendations for IROS 2012 Travel support consideration.


\section*{Project Funding}
\begin{itemize}
\item Agency: U.S. National Science Foundation (NSF)
\item Grant Title: \textit{Partnerships for International Research
and Education (PIRE)}
\item Grant Number: \#0730206
\end{itemize}

\section*{Travel Funding Sources}
Additional travel funding will be provided by the Drexel Autonomous Systems Lab (DASL).  If needed additional support will be provided by the Mechanical Engineering Department, the Electrical and Computer Engineering Department and the College of Engineering at Drexel University.


\end{document}